Compiling refinement types to dependent types

### 2020-07-02 tex/paper.tex
Clarify the syntax for typing contexts
Set up some derived entities in the core language

\newNTclass{nonterm}
\newnonterm e \varepsilon
\newnonterm{eS}{\varepsilon}
\newnonterm{ec}{\overline\varepsilon}
\newnonterm r \rho
\newnonterm{tS}{\tau}
\newnonterm{tC}{\overline\tau}
\newnonterm s s
\newnonterm B B
\newnonterm{G}{\Gamma}
\newnonterm{GC}{\overline\Gamma}
\newnonterm{binop}{\odot}

@@

>>>>

\newNTclass{nonterm}
\newnonterm e \varepsilon
\newnonterm{eS}{\varepsilon}
\newnonterm{ec}{\overline\varepsilon}
\newnonterm r \rho
\newnonterm{tS}{\tau}
\newnonterm{tC}{\overline\tau}
\newnonterm s s
\newnonterm B B
\newnonterm G \Gamma
\newnonterm{GC}{\overline\Gamma}
\newnonterm{binop}{\odot}

@@

We also establish some derived entities in the target language to simplify the subsequent exposition:

\begin{itemize}
  \item Non-dependent function type:
	\[
	  \tau_1 \rightarrow \tau_2 := \Pi x : \tau_1. \tau_2,
	\]
	where $\tau_2$ does not have $x$ free.
  \item Dependent pair type, with the first component being a value $x$ of type $\tau$ and the second component being of type $P x$:
	\[
	  \{ x : \tau\ **\ P x \} := \Pi \alpha : \star. (\Pi x : \tau. P x \rightarrow \alpha) \rightarrow \alpha.
	\]
  \item Accessing the first and second component of the dependent pair:
	\[
	  \text{fst} := TODO,
	\]
	\[
	  \text{snd} := TODO.
	\]
  \item Non-dependent pair type:
	\[
	  (\tau_1, \tau_2) := \{ x : \tau_1\ **\ (\lambda \_ : \tau_1. \tau_2) x \}.
	\]
\end{itemize}
